Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-24 demystify.tex

>>>>

\begin{commentbox}
    [Deepak:]
    In my view, cold emails are not welcome by most faculty members and should be avoided. However, if one is already admitted to a program in some department, by all means, send an email to the faculty you may be interested in working with, but do mention right at the beginning that you are already admitted to the program as well as several other universities. State specific areas (preferably specific topics-ML, robotics instead of AI).
\end{commentbox}
